---
title: "Matrix Algebra Fundamentals"
---

## What is a Matrix?

- A **matrix** is a rectangular array of numbers arranged in rows and columns
- Written using square brackets or parentheses
- Each number in the matrix is called an **element** or **entry**

## What is a Matrix?

$$\mathbf{A} = \begin{bmatrix} 
a_{11} & a_{12} & a_{13} \\
a_{21} & a_{22} & a_{23} \\
a_{31} & a_{32} & a_{33}
\end{bmatrix}$$


## Matrix Dimensions

::: {.fragment}
**Rows** are horizontal ↔
:::

::: {.fragment}
**Columns** are vertical ↕
:::

::: {.fragment}
$$
\mathbf{A} = \begin{bmatrix} 
\require{color}\colorbox{#eec8e1}{$a_{11}$} & \colorbox{#eec8e1}{$a_{12}$} & \colorbox{#eec8e1}{$a_{13}$} \\
a_{21} & a_{22} & a_{23} \\
a_{31} & a_{32} & a_{33}
\end{bmatrix} \leftarrow \text{Row 1}
$$
:::


## Matrix Dimensions

**Rows** are horizontal ↔

**Columns** are vertical ↕

$$
\mathbf{A} = \begin{bmatrix} 
\require{color}a_{11} & a_{12} & a_{13} \\
\colorbox{#eec8e1}{$a_{21}$} & \colorbox{#eec8e1}{$a_{22}$} & \colorbox{#eec8e1}{$a_{23}$} \\
a_{31} & a_{32} & a_{33}
\end{bmatrix} \leftarrow \text{Row 2}
$$

## Matrix Dimensions

**Rows** are horizontal ↔

**Columns** are vertical ↕

$$
\mathbf{A} = \begin{bmatrix} 
\require{color}a_{11} & a_{12} & a_{13} \\
a_{21} & a_{22} & a_{23} \\
\colorbox{#eec8e1}{$a_{31}$} & \colorbox{#eec8e1}{$a_{32}$} & \colorbox{#eec8e1}{$a_{33}$}
\end{bmatrix} \leftarrow \text{Row 3}
$$

## Matrix Dimensions

**Rows** are horizontal ↔

**Columns** are vertical ↕


$$
\mathbf{A} = \begin{bmatrix} 
\colorbox{#eec8e1}{$a_{11}$} & a_{12} & a_{13} \\
\colorbox{#eec8e1}{$a_{21}$} & a_{22} & a_{23} \\
\colorbox{#eec8e1}{$a_{31}$} & a_{32} & a_{33}
\end{bmatrix} \leftarrow \text{Column 1}
$$



## Matrix Size: n × p

::: {.fragment}
A matrix with **n rows** and **p columns** is called an **n × p matrix**
:::

::: {.fragment}
$$\mathbf{A}_{3 \times 3} = \begin{bmatrix} 
a_{11} & a_{12} & a_{13} \\
a_{21} & a_{22} & a_{23} \\
a_{31} & a_{32} & a_{33}
\end{bmatrix}$$

This is a **3 × 3** matrix (3 rows, 3 columns)
:::

## Matrix Size: n × p

A matrix with **n rows** and **p columns** is called an **n × p matrix**


$$\mathbf{B}_{2 \times 4} = \begin{bmatrix} 
b_{11} & b_{12} & b_{13} & b_{14} \\
b_{21} & b_{22} & b_{23} & b_{24}
\end{bmatrix}$$

This is a **2 × 4** matrix (2 rows, 4 columns)



## Examples of Different Matrix Sizes

::: {.column}
::: {.fragment}
**Row vector** (1 × p):
$$\mathbf{r} = \begin{bmatrix} 1 & 3 & 5 & 7 \end{bmatrix}$$
:::

:::

::: {.column}
::: {.fragment}
**Column vector** (n × 1):
$$\mathbf{c} = \begin{bmatrix} 2 \\ 4 \\ 6 \end{bmatrix}$$
:::

:::

## Examples of Different Matrix Sizes


**Square matrix** (n × n):
$$\mathbf{S} = \begin{bmatrix} 
1 & 2 \\
3 & 4
\end{bmatrix}$$




## Matrix Addition

::: {.fragment}
Matrices can be added **only if they have the same dimensions**
:::

::: {.fragment}
Add corresponding elements:
$$\mathbf{A} + \mathbf{B} = \begin{bmatrix} a_{11} + b_{11} & a_{12} + b_{12} \\ a_{21} + b_{21} & a_{22} + b_{22} \end{bmatrix}$$
:::

## Matrix Addition

::: {.fragment}
**Example:**
$$\begin{bmatrix} 1 & 2 \\ 3 & 4 \end{bmatrix} + \begin{bmatrix} 5 & 6 \\ 7 & 8 \end{bmatrix}$$
:::

::: {.fragment}
$$= \begin{bmatrix} \color{red}{1+5} & \color{blue}{2+6} \\ \color{green}{3+7} & \color{purple}{4+8} \end{bmatrix} = \begin{bmatrix} \color{red}{6} & \color{blue}{8} \\ \color{green}{10} & \color{purple}{12} \end{bmatrix}$$
:::

---

## You Try: Matrix Addition

::: {.fragment}
**Problem:** Add these matrices
$\mathbf{A} = \begin{bmatrix} 3 & -1 & 2 \\ 0 & 4 & -3 \end{bmatrix}, \quad \mathbf{B} = \begin{bmatrix} 1 & 2 & -1 \\ 5 & -2 & 1 \end{bmatrix}$
:::

::: {.fragment}
**You Try:** 
$\mathbf{A} + \mathbf{B} = ?$
:::

::: {.fragment}
**Solution:** 
$\mathbf{A} + \mathbf{B} = \begin{bmatrix} 3+1 & -1+2 & 2+(-1) \\ 0+5 & 4+(-2) & -3+1 \end{bmatrix} = \begin{bmatrix} 4 & 1 & 1 \\ 5 & 2 & -2 \end{bmatrix}$
:::

```{r}
#| echo: false
countdown::countdown(4)
```




## Matrix Addition: Dimension Requirements

::: {.column width=60%}
::: {.fragment}

**This works** ✓

::: small
$$\colorbox{#eec8e1}{$\mathbf{A}_{2 \times 3} + \mathbf{B}_{2 \times 3} = \mathbf{C}_{2 \times 3}$}$$
:::
:::
:::

::: {.column width=40%}
::: {.fragment}
**This doesn't work** ✗

::: small
$$\colorbox{#eec8e1}{$\mathbf{A}_{2 \times 3} + \mathbf{B}_{3 \times 2} = \text{?}$}$$
:::
:::
:::

::: {.fragment}
The matrices must have **exactly the same dimensions** to be added!
:::

---

## Matrix Multiplication: The Basics 

* Matrix multiplication is **NOT** element-wise multiplication
* For $\mathbf{A} \times \mathbf{B}$ to be defined the number of **columns in A** must equal number of **rows in B** ([inner dimensions]{.hl} must match!)
* If $\mathbf{A}$ is $m \times n$ and $\mathbf{B}$ is $n \times p$, then:
$$\mathbf{A}_{m \times n} \times \mathbf{B}_{n \times p} = \mathbf{C}_{m \times p}$$



## You Try: Matrix Dimensions

::: {.fragment}
**Problem:** Can these matrices be multiplied? If yes, what's the resulting dimension?

$\mathbf{A}_{3 \times 2} \times \mathbf{B}_{2 \times 4} = ?$

$\mathbf{C}_{2 \times 5} \times \mathbf{D}_{3 \times 2} = ?$
:::


::: {.fragment}
**Solutions:**

1. $\mathbf{A}_{3 \times 2} \times \mathbf{B}_{2 \times 4} = \mathbf{Result}_{3 \times 4}$ ✓ (inner dimensions match: 2 = 2)

2. $\mathbf{C}_{2 \times 5} \times \mathbf{D}_{3 \times 2}$ = undefined ✗ (inner dimensions don't match: 5 ≠ 3)
:::

```{r}
#| echo: false
countdown::countdown(2)
```



## Matrix Multiplication: Step by Step


$$
\begin{bmatrix} 1 & 2 \\ 3 & 4 \end{bmatrix} \times \begin{bmatrix} 5 & 6 \\ 7 & 8 \end{bmatrix}=\begin{bmatrix}&\\&\end{bmatrix}
$$

## Matrix Multiplication: Step by Step


$$
\begin{bmatrix} 1 & 2 \\ 3 & 4 \end{bmatrix} \times \begin{bmatrix} 5 & 6 \\ 7 & 8 \end{bmatrix}=\begin{bmatrix}\colorbox{#eec8e1}{}&\\&\end{bmatrix}
$$

## Matrix Multiplication: Step by Step


$$\begin{bmatrix} \colorbox{#eec8e1}{1} & 2 \\ 3 & 4 \end{bmatrix} \times \begin{bmatrix} \colorbox{#eec8e1}{5} & 6 \\ 7 & 8 \end{bmatrix}=\begin{bmatrix}\colorbox{#eec8e1}{(1)(5)}&\\&\end{bmatrix}$$

## Matrix Multiplication: Step by Step


$$\begin{bmatrix} \colorbox{#eec8e1}{1} & \colorbox{#eec8e1}2 \\ 3 & 4 \end{bmatrix} \times \begin{bmatrix} \colorbox{#eec8e1}{5} & 6 \\ \colorbox{#eec8e1}7 & 8 \end{bmatrix}=\begin{bmatrix}\colorbox{#eec8e1}{(1)(5) + (2)(7)}&\\&\end{bmatrix}$$

## Matrix Multiplication: Step by Step


$$\begin{bmatrix} \colorbox{#eec8e1}{1} & \colorbox{#eec8e1}2 \\ 3 & 4 \end{bmatrix} \times \begin{bmatrix} \colorbox{#eec8e1}{5} & 6 \\ \colorbox{#eec8e1}7 & 8 \end{bmatrix}=\begin{bmatrix}\colorbox{#eec8e1}{19}&\\&\end{bmatrix}$$

## Matrix Multiplication: Step by Step


$$
\begin{bmatrix} 1 & 2 \\ 3 & 4 \end{bmatrix} \times \begin{bmatrix} 5 & 6 \\ 7 & 8 \end{bmatrix}=\begin{bmatrix}19&\colorbox{#eec8e1}{ }\\&\end{bmatrix}
$$

## Matrix Multiplication: Step by Step


$$
\begin{bmatrix} \colorbox{#eec8e1}1 & 2 \\ 3 & 4 \end{bmatrix} \times \begin{bmatrix} 5 & \colorbox{#eec8e1}6 \\ 7 & 8 \end{bmatrix}=\begin{bmatrix}19&\colorbox{#eec8e1}{(1)(6)}\\&\end{bmatrix}
$$

## Matrix Multiplication: Step by Step


$$
\begin{bmatrix} \colorbox{#eec8e1}1 & \colorbox{#eec8e1}2 \\ 3 & 4 \end{bmatrix} \times \begin{bmatrix} 5 & \colorbox{#eec8e1}6 \\ 7 & \colorbox{#eec8e1}8 \end{bmatrix}=\begin{bmatrix}19&\colorbox{#eec8e1}{(1)(6)+(2)(8)}\\&\end{bmatrix}
$$

## Matrix Multiplication: Step by Step


$$
\begin{bmatrix} \colorbox{#eec8e1}1 & \colorbox{#eec8e1}2 \\ 3 & 4 \end{bmatrix} \times \begin{bmatrix} 5 & \colorbox{#eec8e1}6 \\ 7 & \colorbox{#eec8e1}8 \end{bmatrix}=\begin{bmatrix}19&\colorbox{#eec8e1}{22}\\&\end{bmatrix}
$$


## Matrix Multiplication: Step by Step


$$
\begin{bmatrix} 1 & 2 \\ 3 & 4 \end{bmatrix} \times \begin{bmatrix} 5 & 6 \\ 7 & 8 \end{bmatrix}=\begin{bmatrix}19&22{}\\\colorbox{#eec8e1}{ }&\end{bmatrix}
$$

## Matrix Multiplication: Step by Step


$$
\begin{bmatrix} 1 & 2 \\ \colorbox{#eec8e1}3 & 4 \end{bmatrix} \times \begin{bmatrix} \colorbox{#eec8e1}5 & 6 \\ 7 & 8 \end{bmatrix}=\begin{bmatrix}19&22{}\\\colorbox{#eec8e1}{(3)(5) }&\end{bmatrix}
$$

## Matrix Multiplication: Step by Step


$$
\begin{bmatrix} 1 & 2 \\ \colorbox{#eec8e1}3 & \colorbox{#eec8e1}4 \end{bmatrix} \times \begin{bmatrix} \colorbox{#eec8e1}5 & 6 \\ \colorbox{#eec8e1}7 & 8 \end{bmatrix}=\begin{bmatrix}19&22{}\\\colorbox{#eec8e1}{(3)(5) +(4)(7)}&\end{bmatrix}
$$

## Matrix Multiplication: Step by Step


$$
\begin{bmatrix} 1 & 2 \\ \colorbox{#eec8e1}3 & \colorbox{#eec8e1}4 \end{bmatrix} \times \begin{bmatrix} \colorbox{#eec8e1}5 & 6 \\ \colorbox{#eec8e1}7 & 8 \end{bmatrix}=\begin{bmatrix}19&22{}\\\colorbox{#eec8e1}{43}&\end{bmatrix}
$$

## Matrix Multiplication: Step by Step


$$
\begin{bmatrix} 1 & 2 \\ 3 & 4 \end{bmatrix} \times \begin{bmatrix} 5 & 6 \\ 7 & 8 \end{bmatrix}=\begin{bmatrix}19&22{}\\43&\colorbox{#eec8e1}{ }\end{bmatrix}
$$

## Matrix Multiplication: Step by Step


$$
\begin{bmatrix} 1 & 2 \\ \colorbox{#eec8e1}3 & 4 \end{bmatrix} \times \begin{bmatrix} 5 & \colorbox{#eec8e1}6 \\ 7 & 8 \end{bmatrix}=\begin{bmatrix}19&22{}\\43&\colorbox{#eec8e1}{(3)(6) }\end{bmatrix}
$$

## Matrix Multiplication: Step by Step


$$
\begin{bmatrix} 1 & 2 \\ \colorbox{#eec8e1}3 & \colorbox{#eec8e1}4 \end{bmatrix} \times \begin{bmatrix} 5 & \colorbox{#eec8e1}6 \\ 7 & \colorbox{#eec8e1}8 \end{bmatrix}=\begin{bmatrix}19&22{}\\43&\colorbox{#eec8e1}{(3)(6)+(4)(8) }\end{bmatrix}
$$

## Matrix Multiplication: Step by Step


$$
\begin{bmatrix} 1 & 2 \\ \colorbox{#eec8e1}3 & \colorbox{#eec8e1}4 \end{bmatrix} \times \begin{bmatrix} 5 & \colorbox{#eec8e1}6 \\ 7 & \colorbox{#eec8e1}8 \end{bmatrix}=\begin{bmatrix}19&22{}\\43&\colorbox{#eec8e1}{52}\end{bmatrix}
$$


## You Try: Matrix Multiplication

::: {.fragment}
**Problem:** Multiply these matrices
$\mathbf{A} = \begin{bmatrix} 2 & 3 \\ 1 & 4 \end{bmatrix}, \quad \mathbf{B} = \begin{bmatrix} 1 & 0 \\ 2 & 1 \end{bmatrix}$
:::

::: {.fragment}
**You Try:** 
$\mathbf{A} \times \mathbf{B} = ?$
:::

::: {.fragment}
**Solution:** 

$\mathbf{A} \times \mathbf{B} = \begin{bmatrix} 8 & 3 \\ 9 & 4 \end{bmatrix}$
:::

```{r}
#| echo: false
countdown::countdown(5)
```



## Matrix Multiplication: Dimension Examples

::: column
::: {.fragment}
**Valid multiplications:**

- $\mathbf{A}_{2 \times 3} \times \mathbf{B}_{3 \times 4} = \mathbf{C}_{2 \times 4}$ ✓

- $\mathbf{A}_{5 \times 2} \times \mathbf{B}_{2 \times 1} = \mathbf{C}_{5 \times 1}$ ✓

:::
:::

::: column
::: {.fragment}
**Invalid multiplications:**

- $\mathbf{A}_{2 \times 3} \times \mathbf{B}_{4 \times 2}$ ✗ (3 ≠ 4)

- $\mathbf{A}_{3 \times 5} \times \mathbf{B}_{2 \times 3}$ ✗ (5 ≠ 2)
:::
:::

::: {.fragment}
**Remember:** Inner dimensions must match!
:::



## Matrix Transpose

::: {.fragment}
The **transpose** of matrix $\mathbf{A}$ is denoted $\mathbf{A}^T$ or $\mathbf{A}'$
:::

::: {.fragment}

Flip rows and columns

- Row 1 becomes Column 1
- Row 2 becomes Column 2, etc.
:::

## Matrix Transpose 

::: small
::: column
::: {.fragment}

$$\mathbf{A} = \begin{bmatrix} 1 & 2 & 3 \\ 4 & 5 & 6 \end{bmatrix}_{2 \times 3}$$
:::
:::

::: column
::: {.fragment}
$$\mathbf{A}^T = \begin{bmatrix} 1 & 4 \\ 2 & 5 \\ 3 & 6 \end{bmatrix}_{3 \times 2}$$
:::
:::
:::

## You Try: Matrix Transpose

::: {.fragment}
Find the transpose of this matrix
$\mathbf{A} = \begin{bmatrix} 1 & 4 & 7 \\ 2 & 5 & 8 \end{bmatrix}$   $A^T= ?$
:::


::: {.fragment}
**Solution:** 
$\mathbf{A}^T = \begin{bmatrix} 1 & 2 \\ 4 & 5 \\ 7 & 8 \end{bmatrix}$
:::

```{r}
#| echo: false
countdown::countdown(3)
```




## Transpose Properties


If $\mathbf{A}$ is $m \times n$, then $\mathbf{A}^T$ is $n \times m$

## Transpose Properties

1. $(\mathbf{A}^T)^T = \mathbf{A}$

2. $(\mathbf{A} + \mathbf{B})^T = \mathbf{A}^T + \mathbf{B}^T$

3. $(\mathbf{AB})^T = \mathbf{B}^T\mathbf{A}^T$ (order reverses!)
4. **Symmetric Matrix:** $\mathbf{A} = \mathbf{A}^T$

## Symmetric Matrix

$\mathbf{A} = \mathbf{A}^T$


$$\mathbf{S} = \begin{bmatrix} 1 & 2 & 3 \\ 2 & 4 & 5 \\ 3 & 5 & 6 \end{bmatrix}$$



## The Identity Matrix

::: {.fragment}
The **identity matrix** $\mathbf{I}$ is the matrix equivalent of the number 1
:::

::: {.fragment}

- Square matrix with 1's on the diagonal and 0's elsewhere

- Acts as the multiplicative identity: $\mathbf{AI} = \mathbf{IA} = \mathbf{A}$
:::

## The Identity Matrix

$$\mathbf{I}_2 = \begin{bmatrix} \color{red}{1} & 0 \\ 0 & \color{red}{1} \end{bmatrix}, \quad \mathbf{I}_3 = \begin{bmatrix} \color{red}{1} & 0 & 0 \\ 0 & \color{red}{1} & 0 \\ 0 & 0 & \color{red}{1} \end{bmatrix}$$

## The Identity Matrix

**Example:**
$$\begin{bmatrix} 2 & 3 \\ 4 & 5 \end{bmatrix} \begin{bmatrix} 1 & 0 \\ 0 & 1 \end{bmatrix} = \begin{bmatrix} 2 & 3 \\ 4 & 5 \end{bmatrix}$$



## You Try: Identity Matrix

::: {.fragment}
**Problem:** Verify that this multiplication gives the identity property
$\begin{bmatrix} 3 & -1 \\ 2 & 4 \end{bmatrix} \begin{bmatrix} 1 & 0 \\ 0 & 1 \end{bmatrix} = ?$
:::


::: {.fragment}
**Solution:** 
$= \begin{bmatrix} 3 & -1 \\ 2 & 4 \end{bmatrix}$ ✓ (Original matrix unchanged!)
:::

```{r}
#| echo: false
countdown::countdown(3)
```


## Matrix Inverse

::: {.fragment}
The **inverse** of matrix $\mathbf{A}$ is denoted $\mathbf{A}^{-1}$
:::

::: {.fragment}
**Definition:** $\mathbf{AA}^{-1} = \mathbf{A}^{-1}\mathbf{A} = \mathbf{I}$
:::

## Matrix Inverse

::: {.fragment}
**Requirements for inverse to exist:**  
- Matrix must be **square** (n × n)  
- Matrix must be **non-singular** (determinant ≠ 0)
:::

## Matrix Inverse

::: {.fragment}
**2 × 2 Formula:**
For $\mathbf{A} = \begin{bmatrix} a & b \\ c & d \end{bmatrix}$

$$\mathbf{A}^{-1} = \frac{1}{ad - bc} \begin{bmatrix} d & -b \\ -c & a \end{bmatrix}$$
:::


## Matrix Inverse: Example

::: {.fragment}
$$\mathbf{A} = \begin{bmatrix} 2 & 1 \\ 3 & 2 \end{bmatrix}$$
:::

::: {.fragment}
**Step 1:** Calculate determinant
$$\text{det}(\mathbf{A}) = (2)(2) - (1)(3) = 4 - 3 = 1$$
:::

## Matrix Inverse: Example

$$\mathbf{A} = \begin{bmatrix} 2 & 1 \\ 3 & 2 \end{bmatrix}$$

::: {.fragment}
**Step 2:** Apply formula
$$\mathbf{A}^{-1} = \frac{1}{1} \begin{bmatrix} 2 & -1 \\ -3 & 2 \end{bmatrix} = \begin{bmatrix} 2 & -1 \\ -3 & 2 \end{bmatrix}$$
:::

## Matrix Inverse: Example

$$\mathbf{A} = \begin{bmatrix} 2 & 1 \\ 3 & 2 \end{bmatrix}$$

::: {.fragment}
**Verify:**
$$\mathbf{AA}^{-1} = \begin{bmatrix} 2 & 1 \\ 3 & 2 \end{bmatrix} \begin{bmatrix} 2 & -1 \\ -3 & 2 \end{bmatrix} = \begin{bmatrix} 1 & 0 \\ 0 & 1 \end{bmatrix} = \mathbf{I}$$
:::


## You Try: Matrix Inverse

::: {.fragment}
**Problem:** Find the inverse of this matrix
$\mathbf{A} = \begin{bmatrix} 1 & 2 \\ 1 & 3 \end{bmatrix}$
:::

::: {.fragment}
**Solution:** 
1. $\text{det}(\mathbf{A}) = (1)(3) - (2)(1) = 3 - 2 = 1$  
2. $\mathbf{A}^{-1} = \frac{1}{1} \begin{bmatrix} 3 & -2 \\ -1 & 1 \end{bmatrix} = \begin{bmatrix} 3 & -2 \\ -1 & 1 \end{bmatrix}$

**Check:** $\mathbf{AA}^{-1} = \begin{bmatrix} 1 & 2 \\ 1 & 3 \end{bmatrix} \begin{bmatrix} 3 & -2 \\ -1 & 1 \end{bmatrix} = \begin{bmatrix} 1 & 0 \\ 0 & 1 \end{bmatrix}$ ✓
:::

```{r}
#| echo: false
countdown::countdown(6)
```




## Special Matrix Types

::: {.fragment}
**Diagonal Matrix:** Non-zero elements only on the main diagonal

$$\mathbf{D} = \begin{bmatrix} d_1 & 0 & 0 \\ 0 & d_2 & 0 \\ 0 & 0 & d_3 \end{bmatrix}$$
:::

## Special Matrix Types

::: {.fragment}
**Orthogonal Matrix:** $\mathbf{Q}^T\mathbf{Q} = \mathbf{I}$ (columns are orthonormal)
:::

## Special Matrix Types

::: {.fragment}
**Positive Definite:** $\mathbf{x}^T\mathbf{A}\mathbf{x} > 0$ for all $\mathbf{x} \neq \mathbf{0}$
:::

## Special Matrix Types

::: {.fragment}
**Symmetric Matrix:** $\mathbf{A} = \mathbf{A}^T$

:::

## You Try: Special Matrices

::: {.fragment}
**Problem:** Identify the type of each matrix
$\mathbf{A} = \begin{bmatrix} 2 & 0 & 0 \\ 0 & -1 & 0 \\ 0 & 0 & 3 \end{bmatrix}, \quad \mathbf{B} = \begin{bmatrix} 1 & 4 \\ 4 & 2 \end{bmatrix}, \quad \mathbf{C} = \begin{bmatrix} 1 & 2 \\ 3 & 4 \end{bmatrix}$
:::


::: {.fragment}
**Solutions:**
- Matrix A: **Diagonal matrix** (non-zero elements only on main diagonal)
- Matrix B: **Symmetric matrix** ($\mathbf{B} = \mathbf{B}^T$ since $b_{12} = b_{21} = 4$)
- Matrix C: **General matrix** (no special properties)
:::

```{r}
#| echo: false
countdown::countdown(2)
```

